{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras

### 2011-06-02 doc/paper.tex
String and branching functions, multiplicity functions return formalElements, start on work on manual, contents of software package in the paper, comma fix in bibliography.

More complex models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr}.

@@

\newpage
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

@@

\bibliographystyle{elsarticle-num}
\bibliography{bibliography}

>>>>

More complex models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

\section{Software package}
\label{package}
The package can be freely downloaded from {\it github}. Latest release can be found here. To get the development code use the command
\begin{lstlisting}[language=bash]
 git clone git://github.com/naa/Affine.git
\end{lstlisting}

Contents of the package:
\begin{verbatim}
    Affine/                                root folder
      demo/                                  demonstrations
        demo.nb                                demo notebook
        paper.nb                               code from the paper
      doc/                                 documentation folder
        figures/                             figures in paper and manual
          timing.pdf                           diagram showing performance
          branching.pdf                        branching coefficients
        bibliography.bib                     bibliographic database
        manual.pdf                           manual
        manual.tex                           manual source
        paper.pdf                            paper
        paper.tex                            paper source
        TODO.org                             list of issues
      src/                                 source folder
        affine.m                             main software package
      tests/                               unit tests folder
        tests.m                              unit tests
      README.markdown                      short description of software
\end{verbatim}

@@

\section*{References}
\label{sec:references}

\bibliography{bibliography}
\bibliographystyle{elsarticle-num}
%\bibliographystyle{model1-num-names}
